---
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r, eval = T, echo=FALSE, warning=FALSE, message=FALSE}
chapter_index <- "05"
if (exists(paste0("fig_create_", chapter_index))) fig_create <- get(paste0("fig_create_", chapter_index)) else fig_create <- TRUE
if (exists(paste0("fig_fromfile_", chapter_index))) fig_fromfile <- get(paste0("fig_fromfile_", chapter_index)) else fig_fromfile <- FALSE

if (exists(paste0("islatexout"))) islatexout <- get(paste0("islatexout")) else islatexout <- FALSE
```

# Industrial sectors {#indsec}
```{r, results='asis', eval=(islatexout), echo = FALSE}
cat("\\vspace*{-1.5cm}")
```

**Proposed content by Fernando**

- Manufactured products by level of technological content
    - Shares in total manufacturing production and trade through time
    - Contributions by main country groups
    - Highlights (for example, main contributions by category of product, countries that have moved the most in the technological content of their products)
- Manufacturing industries (2-digit ISIC)
    - Shares in total manufacturing through time
    - Contributions by main country groups
    - Highlights (for example, leading economies by industry, countries that have moved the most in specific industries)
    - Analysis of recent events, shocks, policies that have affected specific industries

```{r, results='asis', eval=(islatexout), echo = FALSE}
cat("\\vspace*{\\fill}")
```

```{r, eval = TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.fullwidth = FALSE, fig.margin = FALSE, fig.cap="Sample Figure"}
rel_file_name <- "sample_image.png"
rel_file <- file.path(rel_img_path, rel_file_name)
knitr::include_graphics(rel_file)
``` 

```{r, results='asis', eval=(knitr::opts_knit$get('rmarkdown.pandoc.to') == 'latex'), echo = FALSE}
cat('\\pagebreak')
```

```{r, child = '_common_samplesectionpage.Rmd'}
```

```{r, results='asis', eval=(islatexout), echo = FALSE}
cat('\\clearpage\\pagebreak\n')
cat("\\ChapterEndPage\n")
cat('\\pagebreak\n')
```
